Inspect Different Length Sample Size impact on ISS 1.0

### 2024-09-20 Rmd/Inspect_Outputs/change_sample_size_1.0.Rmd
document mistake: I coded the subsampling routine incorrectly. all 0.5._ scripts are invalid. see those scripts for details. Forward: code subsampling after boot_length instead of inside it.

@@

>>>>

IGNORE THIS SCRIPT!! THE RESULTS ARE INVALID! I DID NOT CODE THE SUBSAMPLING CORRECTLY, I DID NOT USE SIZE ARGUEMENT IN SAMPLE.INT LIKE I SHOULD HAVE. WHEN I TRIED TO USE IT, BOOT_LENGTH WOULD NOT WORK BECAUSE MUTATE CANNOT ACCEPT UNEQUAL LENGTH VECTORS TO WHAT IT IS ASKED TO REPLACE.

@@

UPDATE: THIS OUTPUT IS INNACURATE! I DID NOT CODE THE SAMPLING ROUTINE CORRECTLY: IT DOES NOT SUBSAMPLE, RATHER IT TAKES .N IN BOTH CASES WHEN I INTENDED OTHERWISE.
